\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-06-28 manuscript/manuscript.tex
updated grammar

	\caption{Principal component analysis of pan-cancer cell line therapeutic efficacy, generated from IC$_{50}$ values of all available chemotherapeutics.The horizontal axis shows the first principal component, the vertical axis the second component. Cell lines are visualized based on major cancer type classifications, including (\textbf{A}) body system of tumour and (\textbf{B}) solid vs. non-solid tumour status. Cell lines were also visualized on major molecular markers, including (\textbf{C}) TP53 mutation status, and (\textbf{D}) KRAS mutation status.}
	\label{fig:overall_pca}
\end{figure*}

@@

    \caption{(\textbf{A}) Principal component analysis of pan-cancer cell line therapeutic efficacy, generated from IC$_{50}$ values of all available chemotherapeutics. The horizontal axis shows the first principal component, the vertical axis the second component. The two identified therapeutic response clusters are indicated in red and blue respectively. (\textbf{B}) Volcano plot identifying chemotherapeutics with significantly different IC$_{50}$ values between therapeutic response clusters. Drugs identified in red meet the criteria for significance (FDR adjusted $p<0.05$). (\textbf{C}) Heatmap of therapeutic IC$_{50}$ for the two identified therapeutic response clusters. Columns represent individual chemotherapies and are clustered according to Euclidean distance. Colours range from yellow to black, with a shift toward the latter indicating increased efficacy of the corresponding chemotherapeutic.}
    \label{fig:clustering}
\end{figure*}

>>>>

	\caption{Principal component analysis of pan-cancer cell line therapeutic efficacy generated from IC$_{50}$ values of all available chemotherapeutics.The horizontal axis shows the first principal component, the vertical axis the second component. Cell lines are visualized based on major cancer type classifications, including (\textbf{A}) body system of tumour and (\textbf{B}) solid vs. non-solid tumour status. Cell lines were also visualized on major molecular markers, including (\textbf{C}) TP53 mutation status, and (\textbf{D}) KRAS mutation status.}
	\label{fig:overall_pca}
\end{figure*}

@@

    \caption{(\textbf{A}) Principal component analysis of pan-cancer cell line therapeutic efficacy generated from IC$_{50}$ values of all available chemotherapeutics. The horizontal axis shows the first principal component, the vertical axis the second component. The two identified therapeutic response clusters are indicated in red and blue respectively. (\textbf{B}) Volcano plot identifying chemotherapeutics with significantly different IC$_{50}$ values between therapeutic response clusters. Drugs identified in red meet the criteria for significance (FDR adjusted $p<0.05$). (\textbf{C}) Heatmap of therapeutic IC$_{50}$ for the two identified therapeutic response clusters. Columns represent individual chemotherapies and are clustered according to Euclidean distance. Colours range from yellow to black, with a shift toward the latter indicating increased efficacy of the corresponding chemotherapeutic.}
    \label{fig:clustering}
\end{figure*}
